#Reproducible Research Project 1
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
library(ggplot2)
library(scales)
library(Hmisc)
```
## Loading and preprocessing data
##### 1. Load the data (i.e. read.csv())
```{r, results='markup', warning=TRUE, message=TRUE}
if(!file.exists('activity.csv')){
  unzip('activity.zip')
}
activityData <- read.csv('activity.csv')
```
##### 2. Process/transform the data (if necessary) into a format suitable for your analysis
```{r}
#activityData$interval <- strptime(gsub("([0-9]{1,2})([0-9]{2})", "\\1:\\2", activityData$interval), format='%H:%M')
```
## What is mean total number of steps taken per day?
```{r}
stepsByDay <- tapply(activityData$steps, activityData$date, sum, na.rm=TRUE)
```

##### 1. Make a histogram of the total number of steps taken each day
```{r}
qplot(stepsByDay, xlab='Total steps per day', ylab='Frequency using binwith 500', binwidth=500)
```

##### 2. Calculate and report the mean and median total number of steps taken per day
```{r}
stepsByDayMean <- mean(stepsByDay)
stepsByDayMedian <- median(stepsByDay)
```
# Mean: `r stepsByDayMean`
# Median:  `r stepsByDayMedian`



